### 2014-10-28 Draft/introduction.tex
ignored generated files
Added context of type enforcement and search space explosion

%First, relying just on type information will result in an incomplete list of temporal constraints. In typed languages some temporal constraints are enforced by type system. For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$). However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously. We propose to address the issue by augmenting the type definitions based temporal constraints with the constraints inferred from the natural language text in API documents. Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse for a strongly typed language. The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}. Our proposed approach extends the existing approaches to address the challenge.

>>>>

%First, relying just on type information will result in an incomplete list of temporal constraints. 
In traditional API, which are usually implemented in typed languages some temporal constraints are enforced by type system itself.
Voilations are easily detected by the IDE's
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates
that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
However, using type system to detect temporal constraints in context of web APIs will result
in a lot of false positives as web APIs work only on basic types such as
\CodeIn{strings} and \CodeIn{numbers}.
Use of basic datatype by web-apis result in search space explosion.
Furthermore, we observed that temporal constraints re not limited to the type definitions

Our proposed approach extends the existing approaches to address the challenge.

However, temporal constraints are not limited by the type definitions
(i.e, requirements on the type of input parameters),
and are currently expressed mostly in natural language in API documents,
as described in the example previously.
We propose to address the issue by augmenting the type definitions based temporal constraints
with the constraints inferred from the natural language text in API documents.
Furthermore, such constraints although valuable but are already checked by any advanced 
Integrated Development Environment(IDE) such as eclipse for a strongly typed language.
